### 2018-02-09 Maths Notes/Further Pure/FP2/Second Order Differential Equations/Second Order Differential Equations.tex
2nd ODE Notes

>>>>

\textit{When y=1 x=0 $\frac{dy}{dx}=0$}
$$\frac{d^2y}{dx^2}+5\frac{dy}{dx}+6y=12e^x$$
Find the complementary function
$$y=Ae^{-3x}+Be^{-2x}$$
Find the general form of the particular integral
$$PI: \ \lambda e^x$$
Differentiate the particular integral twice
$$\frac{dy}{dx}=\lambda e^x$$
$$\frac{d^2y}{dx^2}=\lambda e^x$$
Substitute into the initial formula
$$\lambda e^5+5\lambda e^x+6\lambda e^x=12e^x$$
Simplify to find lambda
$$12\lambda e^x=12e^x \quad	\lambda=1$$
Add this to the complementary function to find the general solution
$$GS:\ Ae^{-3x}+Be^{-2x}+e^x$$
Substitute y=1 and x=0 into the general solution
$$1=A+B+1$$
$$A+B=0$$
Substitute $\frac{dy}{dx}=0$ and $x=0$ into the differentiated form of the general solution\\
Differentiate the general solution
$$\frac{dy}{dx}=-3Ae^{-3x}-2Be^{-2x}+e^x$$
Substitute values
$$0=-3A-2B+1$$
Solve simultaneous equations
$$A=1 \quad B=-1$$
Substitute into the general solution to find the particular solution
$$PS: \ y=e^{-3x}-e^{-2x}+e^x$$
